### 2019-05-10 tii/tex/motivation.tex
Shorten all

\section{Background and Observations}

@@

In large scale data parallel computing, shuffle is designed to achieve an all-to-all data transfer among nodes. 
For a clear illustration, we use \textit{map tasks} to define the tasks that produce shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
% Note that one task may have both shuffle data generation and consumption in modern DAG framework. These tasks contain characteristic of both map task and reduce task. But these tasks won't change the behavior of shuffle. To avoid ambiguity, in the following paper, we will only use term of map task to represent those who produce shuffle output, and reduce task to represent those who consume shuffle output.
% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{fig/shuffle_process}
% 	\caption{Shuffle Overview}
% 	\label{fig:shuffle_process}
% \end{figure}

@@

\subsubsection{Overview of shuffle process}
Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
The total number of buckets equals the number of reduce tasks in the successive step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

@@

\subsubsection{Impact of shuffle process}
{\color{blue}
Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time.
% For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
% For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
}

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
Can we mitigate or even remove the overhead of shuffle? 
To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
{\color{blue}
As shown in Figure \ref{fig:util}, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
Both \textit{shuffle write} and \textit{shuffle read} occupy the slot without significantly involving CPU.
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization.

@@

% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
	\label{fig:util}
	\vspace{-1em}
\end{figure}

>>>>

\section{Background and Observations}\label{motivation}

@@

{\color{black}
In large scale data parallel computing, shuffle is designed to achieve an all-to-all data transfer among nodes.
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.
Thus, Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate the completion time of jobs.
}
% For a clear illustration, we use \textit{map tasks} to define the tasks that produce shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
% Note that one task may have both shuffle data generation and consumption in modern DAG framework. These tasks contain characteristic of both map task and reduce task. But these tasks won't change the behavior of shuffle. To avoid ambiguity, in the following paper, we will only use term of map task to represent those who produce shuffle output, and reduce task to represent those who consume shuffle output.
% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{fig/shuffle_process}
% 	\caption{Shuffle Overview}
% 	\label{fig:shuffle_process}
% \end{figure}

@@

% \subsubsection{Overview of shuffle process}
% Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
% The total number of buckets equals the number of reduce tasks in the successive step.
% % shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
% The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
% Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
% Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

@@

% \subsubsection{Impact of shuffle process}
% {\color{black}
% Shuffle is I/O intensive, which might introduce a significant latency to the application. 
% Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
% For those shuffle-heavy jobs, the shuffle latency may even dominate the completion time of jobs.
% For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
% For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
% }

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
Can we mitigate or even remove the overhead of shuffle?
To analyze the design and implementation of shuffle, we run some Spark's \textit{GroupByTest} on a 5-node m4.xlarge EC2 cluster.
% To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Figure \ref{fig:util} shows the hardware utilization trace of one node of the experiment.
% Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
{\color{black}
As shown in Figure \ref{fig:util}, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
Both \textit{shuffle write} and \textit{shuffle read} occupy the slot without significantly involving CPU.
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization.

@@

% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
